\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{enumitem}




% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[IoTDI'18]{ACM IoTDI Conference}{July 2018}{Orlando, Florida USA} 
\acmYear{2018}
\copyrightyear{2018}

%\acmPrice{15.00}


\begin{document}
%\title{Device Anomaly detection using Provenance Graphs}
\title{  IoT Device Anomaly Detection using Provenance Graphs}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Ebelechukwu Nwafor}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Howard University}
% \streetaddress{P.O. Box 1212}
  \city{Washington} 
  \state{DC} 
  \postcode{20059}
}
\email{ebelechukwu.nwafor@bison.howard.edu}

\author{Gedare Bloom}
%\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{Howard University}
%  \streetaddress{P.O. Box 1212}
  \city{Washington} 
  \state{DC} 
  \postcode{20059}
}
\email{gedare.bloom@howard.edu}

%\author{Lars Th{\o}rv{\"a}ld}
%\authornote{This author is the
%  one who did all the really hard work.}
%\affiliation{%
%  \institution{The Th{\o}rv{\"a}ld Group}
%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%  \city{Hekla} 
%  \country{Iceland}}
%\email{larst@affiliation.org}
%
%\author{Lawrence P. Leipuner}
%\affiliation{
%  \institution{Brookhaven Laboratories}
%  \streetaddress{P.O. Box 5000}}
%\email{lleipuner@researchlabs.org}
%
%\author{Sean Fogarty}
%\affiliation{%
%  \institution{NASA Ames Research Center}
%  \city{Moffett Field}
%  \state{California} 
%  \postcode{94035}}
%\email{fogartys@amesres.org}
%
%\author{Charles Palmer}
%\affiliation{%
%  \institution{Palmer Research Laboratories}
%  \streetaddress{8600 Datapoint Drive}
%  \city{San Antonio}
%  \state{Texas} 
%  \postcode{78229}}
%\email{cpalmer@prl.com}
%
%\author{John Smith}
%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
%\email{jsmith@affiliation.org}
%
%\author{Julius P.~Kumquat}
%\affiliation{\institution{The Kumquat Consortium}}
%\email{jpkumquat@consortium.net}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}

The Internet of Things (IoT) has revolutionized the way we interact with devices. Unfortunately, this technological advancement has been met with privacy and security challenges. One major concern is the notion of malicious intrusions. A common way of detecting a malicious intrusion is by treating an attack as an  anomaly and using anomaly detection techniques to pinpoint the source of an intrusion. In a given IoT device, provenance graphs which denotes causality between system events offers immense benefit for intrusion detection. Provenance provides a comprehensive history of activities performed on a system which indirectly ensures device trust. Given a provenance graph, how can we determine if an anomalous activity has occurred? This paper seeks to address this issue. In this paper, we propose two lightweight approach to intrusion detection on IoT devices. The first is a whitelist approach which involves matching patterns of known normal provenance graph. The provenance graph exhibiting normal execution of IoT applications are stored in a knowledge repository. Incoming provenance graphs of similar applications are compared with provenance graph in the knowledge repository to determine if they exhibit anomalous behaviors. The second approach involves the use of a similarity metric to compare provenance graphs from the learning and detection phase. We evaluate the performance of our approach by comparing provenance graphs generated from sample IoT applications and determine the number of false positive, and false negative rates.

%We compare our method to two known anomaly detection algorithms. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 




%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Cyber physical systems~Internet of Things</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Information Science ~Data Provenance</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Computer Applications ~Access Control</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>  
%\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Security and privacy~Anomaly detection systems}
 

% We no longer use \terms command
%\terms{Theory}

\keywords{Internet of Things, Provenance Graphs, Anomaly Detection}


\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography} 

\end{document}
